Variation in distance between consecutive animal locations

### 2021-03-31 distributions_paper/rudolph_distributions.Rmd
explore angles

[@kareiva1983analyzing] - approximating displacements by connecting a series of straight lines, and thus summarize animal movement based on parameters for movement length and turning angle. 
*Would be interesting to add a figure with what I am actually analyzing. So, visually show how the gps locations get turned into straight lines, and angles, with an associated time interval. Or we could just multiply everything? So have it all for 15 minute intervals, and then repeat the ones that went on longer, perhaps set a limit for 60 minutes?*

"We know these simple correlated random walks, or simple movement models might not be enough to describe net displacements under more complex processes, for which developments in higher order markov processes show to be promising. However, our goal in this study was to use a simpler model and focus on potential differences when analyzing complete pooling versus no pooling data. In the context of animal-mediated seed dispersal, understanding these indivdiual level differences can help us describe and characterize the implications that different animals may have over spatial distributions of plant populations, and thus identify potential dispersers with higher or more importance, particularly when associated to long-distance seed dispersal events."

@@

>>>>

[@kareiva1983analyzing] - approximating displacements by connecting a series of straight lines, and thus summarize animal movement based on parameters for movement length and turning angle. Using square displacement instead of linear displacement, because it's expectation can be calculated from turning angles and step lengths. Assume that the length of each move and the turning angle are independent random variables, each with its own probability density. Assume that a series of moves can be represented by random draws from these probability densities, and since each random draw is independent from the preceding ones, the random draw process is a first order markov chain. The result is a correlated random walk, and the distribution g(theta) gives a measure of the degree to which the angles of movement are correlated.
*Would be interesting to add a figure with what I am actually analyzing. So, visually show how the gps locations get turned into straight lines, and angles, with an associated time interval. Or we could just multiply everything? So have it all for 15 minute intervals, and then repeat the ones that went on longer, perhaps set a limit for 60 minutes?*

"We know these simple correlated random walks, or simple movement models might not be enough to describe net displacements under more complex processes, for which developments in higher order markov processes show to be promising. However, our goal in this study was to use a simpler model and focus on potential differences when analyzing complete pooling versus no pooling data. In the context of animal-mediated seed dispersal, understanding these indivdiual level differences can help us describe and characterize the implications that different animals may have over spatial distributions of plant populations, and thus identify potential dispersers with higher or more importance, particularly when associated to long-distance seed dispersal events." Written by Javi

@@

```{r}
df %>% 
  ggplot(., aes(x = abs.angle)) +
  geom_histogram() +
  facet_wrap(~Bird_ID)
```

```{r}
df %>%
  drop_na(rel.angle) %>%
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>%
  ggplot(., aes(x = d.angle)) +
  #facet_wrap(~id) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none")
```
